
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Writing a DMS Plan


 DMS elements
   - less than 2 pages
   - Initially not public now.. but may in the future (so don't include anything confidential or proprietary)
    1. Data type
    2. tools/code (note code is not required to be shared)
    3. standards
    4. data preservation, access, timelines
      - no later than the time of publication of findings or the end of the award (whatever comes first) This probably stresses people out... maybe you can justify longer timelines? 
      - renewals can have updated DMS plan with a different timeline, but if not approved must use previous DMS date
      - no cost extension also allows for more time
    5. access, distribution, reuse
      - no specification of how long need to be available, journals may have other requirements
    6. oversight - who will compliance be managed by

## List of references for your DMS Plan

The following are scientific papers that can be referenced in your DMS Plan:

-
-
- 

 



















```{r}
devtools::session_info()
```
