
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```


# (PART\*) DMS Submission Process {-}

```{r, echo=FALSE, fig.alt='Pathway of topics covered in this course: Submission', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g16b04bd80e5_4_113")
```

# Presubmission Tips


- Extramural (grants)
    - DMS plans should be included within the “Other Plan(s)" field on the following forms:

 - for grants not related to career development: [PHS 398 Research Plan](https://grants.nih.gov/grants/how-to-apply-application-guide/forms-h/general-forms-h.pdf).
        - for career development grants: [PHS 398 Career Development Award Supplemental Form](https://grants.nih.gov/grants/how-to-apply-application-guide/forms-h/career-forms-h.pdf).
    - A brief summary and associated costs should be submitted as part of the budget and budget justification.
- Extramural (contracts)
  - DMS plans should be included as part of the technical evaluation
- Intramural
  - Check with the Intramural Research Program
- Other funding agreements
  - Plans should be submitted prior to the release of funds

## Other Submission Tips:

- Resource sharing plans will not be going away (but will **not** be about data and will instead focus on tools and model organisms)
- There will not be a separate [genomic data sharing](https://sharing.nih.gov/genomic-data-sharing-policy/about-genomic-data-sharing/gds-policy-overview) plan. Genomic data sharing plans should simply be included in the overall DMS plan.

## List of references for your DMS Plan

It's always a good idea to read the primary literature! The following are scientific papers that can be referenced in your DMS Plan or read for further context:

- @bonomi_citation_2020 - The promises and challenges associated with sharing genomic data
- @cosgriff_citation_2020 - The promise of shared data for addressing public health emergencies, such as the SARS-CoV-2 pandemic
- @mckiernan_citation_2016 - Data sharing can help advance careers through increases in citations, media attention, potential collaborators, job opportunities, and funding opportunities
- @piwowar_citation_2011 - Investing in data storage and archiving is a good investment of grant funds
- @tenopir_citation_2020 - Most scientists view data sharing favorably; A majority feel lack of access impedes scientific progress
- @vesteghem_citation_2020 - Findable, Accessible, Interoperable and Reusable (FAIR) Data Principles and their importance to precision oncology
- @wilkinson_citation_2016 - Good data management is key to knowledge discovery and innovation; four foundational principles — Findability, Accessibility, Interoperability, and Reusability — can help guide data producers and publishers


# Post Submission Tips

```{r, echo=FALSE, fig.alt='Pathway of topics covered in this course: Post Submission', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g16b04bd80e5_4_138")
```


- You can update your DMS plan if is not accepted during the [Just-in-Time](https://grants.nih.gov/grants/policy/nihgps/HTML5/section_2/2.5.1_just-in-time_procedures.htm) process
- You can also update your DMS plan during regular reporting intervals (but these changes will need to be approved)
- Investigators are expected to report progress made on data sharing in their Research Progress Performance Report (RPPR)
  


