
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```


# (PART\*) DMS Submission Process {-}


# Presubmission Tips

In this section we will outline how you can submit your DMS plan: 

```{r, echo=FALSE, fig.alt='We are on the sixth step of our pathway - Submission', out.width = '80%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g16b04bd80e5_4_113")
```

## Submission by Funding Type

It is important to note that the submission process may be different depending on what type of grant your are applying for:

- Extramural (grants)
  - DMS plans should be included within the “Other Plan(s)" field on the following forms:
    - For grants not related to career development: [PHS 398 Research Plan](https://grants.nih.gov/grants/how-to-apply-application-guide/forms-h/general-forms-h.pdf).
    - For career development grants: [PHS 398 Career Development Award Supplemental Form](https://grants.nih.gov/grants/how-to-apply-application-guide/forms-h/career-forms-h.pdf).
    - A brief summary and associated costs should be submitted as part of the budget and budget justification.
- Extramural (contracts)
  - DMS plans should be included as part of the technical evaluation
- Intramural
  - Check with the Intramural Research Program
- Other funding agreements
  - Plans should be submitted prior to the release of funds

<div class = "notice"> 
- Resource sharing plans will not be going away (but will **not** be about data and will instead focus on tools and model organisms)
- There will **not** be a separate [genomic data sharing](https://sharing.nih.gov/genomic-data-sharing-policy/about-genomic-data-sharing/gds-policy-overview) plan. Genomic data sharing plans should simply be included in the overall DMS plan.
</div>


# Post Submission Tips

In this section we will discuss tips about what might be needed after you submit your DMS plan: 

```{r, echo=FALSE, fig.alt='We are on the final step of our pathway - Post Submission', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g16b04bd80e5_4_138")
```

- You can update your DMS plan if is not accepted during the [Just-in-Time](https://grants.nih.gov/grants/policy/nihgps/HTML5/section_2/2.5.1_just-in-time_procedures.htm) process
- You can also update your DMS plan during regular reporting intervals, but these changes will need to be approved by program staff. Researchers are encouraged to discuss such changes in advance.
  - Examples of appropriate changes include:
    - change in type of data generated
    - a more appropriate data repository becomes available
    - sharing timeline shifts
- Investigators are expected to report progress made on data sharing in their annual Research Progress Performance Report (RPPR)
   - NIH staff will monitor compliance with the DMS plan during this process

```{r, echo=FALSE, fig.alt='DMS plans can be edited during the Just In Time process or during regular reporting intervals, so it is okay if you need to make changes when you learn of better alternatives.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g18159f1730a_67_115")
```
