
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```


# (PART\*) DMS Submission Process {-}

# Presubmission Tips

 Implementation details
- other plans field added to forms H filed of the PHS 398 research plan form/career development supplemental form
- Resource sharing plans will not be going away (but will not be about data - tools and model organisms)- instructions will be updated
- No longer separate data sharing or genomic data sharing plans



this is from the website:

The DMS Plan should be submitted as follows:

- Extramural (grants): DMS Plans should be included within the “Other Plan(s) field on the PHS 398 Research Plan or PHS 398 Career Development Award Supplemental Form. Additionally, a brief summary and associated costs should be submitted as part of the budget and budget justification (see Budgeting for Data Management and Sharing).
- Extramural (contracts): as part of the technical evaluation
- Intramural: determined by the Intramural Research Program
- Other funding agreements: prior to the release of funds

# Post Submission Tips



- can update plan if not accepted (just in time)
- can also update during regular reporting intervals - thus need to show that you made a plan but it's OK if things change (but these will need to be approved)
    
 11. Other details
 -Unique persistent identifiers are not required (such as a DOI but they are encouraged)
  
  Investigators are expected to report progress made on data sharing in their Research Progress Performance Report (RPPR). 
  

 




```{r}
devtools::session_info()
```
