---
title: "NIH Data Management and Sharing Policy"
date: "`r format(Sys.time(), '%B %d, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: book.bib
biblio-style: apalike
link-citations: yes
description: Description about Course/Book.
favicon: assets/favicon.ico
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "bookdown", "knitr", "rmarkdown"
), "packages.bib")
```


# About this Course {-}

The [National Institutes of Health (NIH)](https://www.nih.gov/) is rolling out a new policy for the management and sharing of scientific data starting for (most) grants submitted **January 25, 2023** or later.

The main requirement of this new policy is that researchers include a Data Management and Sharing (DMS) plan with their proposal. **Not all research will require data sharing.** However, everyone must provide a justification if they can't share their data.

Once a DMS plan is accepted by the funding agency, the researchers will be required to carry out the plan. However, updates can be made to the plan as well during the [Just-in-Time process](https://grants.nih.gov/grants/policy/nihgps/html5/section_2/2.5.1_just-in-time_procedures.htm).

In this course we will describe what the new policy requires, places where you might want to share your particular kind of data, and how to deal with possible challenges associated with the policy.

```{r, echo=FALSE, fig.alt='Main topics covered in this course: Introducing the DMS policy, Creating a DMS plan, DMS submission process.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g1784801ac8b_42_26")
```

## Motivation

Navigating the new NIH Data Management and Sharing Policy - [`https://sharing.nih.gov/`](https://sharing.nih.gov/) - can be confusing. We want to help make the process of compliance with this new policy easier. 


## Target Audience  

The course is intended for anyone who plans to submit a grant proposal to the NIH after January 25th, 2023.


## Curriculum  

The course will cover:

- Motivations behind the new policy
- Overview of the new policy requirements and how it may affect you
- Suggestions about where to share your data
- Recommendations about how to budget for your data
- Guidance about how to write a DMS plan
- Information on how to submit the DMS plan to funding agencies
- Guidance on how to update a DMS plan after submission or funding
- General tips and frequently asked questions

<br>

```{r, echo=FALSE, fig.alt='Pathway of more specific topics covered in this course: motivations of the new policy, personal considerations, data storage options, budgeting, creating a DMS plan, submission tips, and post submission tips.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1luFoDzF6aDJEebbL6iWoJ_s8s9nQnaWLL5jghbmWdak/edit#slide=id.g1784801ac8b_42_0")
```

## Overall Takeaways

<div class = motivations>
**Why this change?** As of January 23, 2023, the NIH is requiring all grant proposals include a Data Management and Sharing Plan to aid in the transparency and reproducibility of NIH-funded research.
</div>

<div class = question_box>
**Does this apply to me?** This will apply to most grants that create data, although some grant mechanisms and some data are exempt. **It is not required to share all data**, however a justification is required. Reasons not to share that are acceptable may be ethical, technical, or legal.
</div>

<div class = data>
**Where should I share my data?** The NIH has lists of suggested repositories, and you will need to choose the most appropriate. If there is not an appropriate repository, you can share your data at an institutional (if available) or generalist repository.
</div>

<div class = money>
**How do I budget this?** You may request funds for data management and sharing in direct costs. You may not infrastructure costs in direct costs as these should be included as indirect costs.
</div>

<div class = plan>
**How do I write my plan?** Your plan should be < 2 pages and include sections on data type; tools, software, and code; standards; data preservation, access, and timelines; access, distribution, and reuse considerations; and oversight. **You can change your plan** in the just-in-time process or during regular reporting intervals.
</div>

<div class = submit>
**Will my plan influence my grant score?** Although the Data Management and Sharing Plan is a mandatory part of most grant proposals, it will not be shared with reviewers and thus will not influence your score, however the budget will be visible to reviewers.
</div>

## Authors

This course was developed by the [Fred Hutch Data Science Lab](https://hutchdatascience.org/). Please see the [author credits](#about-the-authors) for more information.
